### 2022-08-25 title/title.tex
more

\vspace*{2\bigskipamount}

@@

%% Uncomment the following lines to insert a vertically centered picture into
%% the title page.
%\vfill
%\includegraphics{title}
\vfill

@@

{\Large\titlefont\bfseries Proefschrift}

@@

ter verkrijging van de graad Doctor

aan de Vrije Universiteit Amsterdam,

@@

ten overstaan van de promotiecommissie van de Faculteit der Bètawetenschappen

op dinsdag 18.10.2022. om 13.15 uur

@@

%% Print the full name of the author.
\makeatletter
{\Large\titlefont\bfseries\@firstname\ \titleshape{\MakeUppercase{\@lastname}}}
\makeatother

Master of Science in Computer Science, \\
Vrije Universiteit Amsterdam, Nederland,

geboren te Belgrado, Servi\"e.

@@

%% The following line is dictated by the promotieregelement.
\noindent Dit proefschrift is goedgekeurd door de

%% List the promotors (supervisors).
\medskip\noindent
\begin{tabular}{ll}
    promotor: & prof.$\,$dr. W. J. Fokkink \\
    copromotoren: & dr. J. C. Blanchette \\
                  & prof.$\,$dr. S. Schulz
\end{tabular}

\bigskip
\noindent Samenstelling promotiecommissie:

%% List the committee members, starting with the Rector Magnificus and the
%% promotor(s) and ending with the reserve members.
\medskip\noindent
\begin{tabular}{p{4.5cm}l}

prof.$\,$dr. M. Hoogendoorn & Vrije Universiteit Amsterdam \\
dr. K. Korovin & The University of Manchester \\
dr. R. Piskac & Yale University \\
dr. A. Steen & University of Greifswald \\
dr. M. Suda & Czech Technical University in Prague \\
prof.$\,$dr. G. Sutcliffe & University of Miami \\

@@

@@

\medskip
\medskip
% TODO Include http://www.win.tue.nl/ipa/?page_id=309
\noindent The work in the thesis has been carried out under the auspices of the research school IPA
(Institute for Programming research and Algorithmics).

>>>>

VRIJE UNIVERSITEIT

\vspace*{4\bigskipamount}

@@

%% Uncomment the following lines to insert a vertically centered picture into
%% the title page.
%\vfill
%\includegraphics{title}
% \vfill
\vspace*{5\bigskipamount}

@@

{ACADEMISCH PROEFSCHRIFT}

@@

ter verkrijging van de graad Doctor aan

de Vrije Universiteit Amsterdam,

@@

ten overstaan van de promotiecommissie

van de Faculteit der Bètawetenschappen

op dinsdag 18 oktober 2022 om 13.45 uur

@@

\smallskip

Petar Vukmirovi\'c

\smallskip

geboren te Belgrado, Servi\"e

@@

%% The following line is dictated by the promotieregelement.

%% List the promotors (supervisors).
\medskip\noindent
\begin{tabular}{ll}
    promotor: & prof.$\,$dr. W. J. Fokkink \\[4\jot]
    copromotoren: & dr. J. C. Blanchette \\
                  & prof.$\,$dr. S. Schulz \\[4\jot]
    promotiecommissie: & prof.$\,$dr. M. Hoogendoorn  \\
                      & dr. K. Korovin               \\
                      & dr. R. Piskac                \\
                      & dr. A. Steen                 \\
                      & dr. M. Suda                  \\
                      & prof.$\,$dr. G. Sutcliffe    \\

@@

% \bigskip
% \noindent Promotiecommissie:

% %% List the committee members, starting with the Rector Magnificus and the
% %% promotor(s) and ending with the reserve members.
% \medskip\noindent
% \begin{tabular}{p{4.5cm}l}

% prof.$\,$dr. M. Hoogendoorn & Vrije Universiteit Amsterdam \\
% dr. K. Korovin & The University of Manchester \\
% dr. R. Piskac & Yale University \\
% dr. A. Steen & University of Greifswald \\
% dr. M. Suda & Czech Technical University in Prague \\
% prof.$\,$dr. G. Sutcliffe & University of Miami \\

% \end{tabular}

@@

\newpage
% TODO Include http://www.win.tue.nl/ipa/?page_id=309
\noindent The work in the thesis has been carried out under the auspices of the research school IPA
(Institute for Programming research and Algorithmics).
